Maragra-CISM status report

### 2017-08-22 README.Rmd
making folders visible through gitignores

# Maragra and malaria

_Joe Brew, Elisa Sicuri, Laia Cirera, Kizito Gondo, Elton Dorkin_

>>>>

# Malaria and sugar
_An in-depth examination of the effect of malaria control activities on the health and productivity of Maragra sugarcane factory workers_

# Purpose

This code repository serves as the "research compendium" for the analysis of Maragra malaria incidence, malaria control, and worker absenteeism and productivity data. The purpose of this repository - which takes the form of a fully documented R package - is "to integrate the computations and code used in data analyses, methodological descriptions, simulations, etc. with the documents that describe and rely on them" ([Gentleman and Lang, 2004](http://biostats.bepress.com/bioconductor/paper2/)). By using this package, anyone (with access to the original data in its original form) will be able to reproduce every step of the analysis and mansucript writing.

# Instructions

1. Clone this repository (using the following code in bash).

```
$ git clone https://github.com/joebrew/maragra
```

2. Install the code in the repository as an R package.

```
# !/usr/bin/R
devtools::install('maragra')
devtools::document('maragra')
```

3.

```

```
